---
title: "Title here"
output: 
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
author: |
  | Mona Mousavi, Taro Mieno^[Corresponding author: tmieno2@unl.edu], David S. Bullock
  | $^1$University of Nebraska Lincoln,  $^2$University of Nebraska Lincoln, $^3$University of Illinois
abstract: |
  Your abstract goes here...
bibliography: PA.bib
csl: american-journal-of-agricultural-economics.csl
fontsize: 12pt
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{setspace}\doublespacing
  \usepackage{lineno}
  \linenumbers
---

```{r echo = F, cache = F, include = F}
library(knitr)
library(here)

here::i_am("GitControlled/Writing/manuscript_ajae.rmd")

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = T,
  echo = F,
  error = T,
  fig.cap = T
)
```

```{r cache = F, include = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(officedown)
library(officer)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(gridExtra)
```

```{r figure_setup, cache = F}
#* +++++++++++++++++++++++++++++++++++
#* Default figure setting
#* +++++++++++++++++++++++++++++++++++
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

 
**Keywords**: 

**Acknowledgement**: This research was supported by ....

# Introduction


# Methods: Monte Carlo Simulation

In our Monte Carlo simulations, .... All the the codes that implement the MC simulation analysis to reproduce the results presented in this study are publicly accessible at <span style = "color: blue;"> Github account</span>.

# Results and Discussions

# Conclusions

<!--
# /*===========================================================
#' # References
# /*===========================================================
-->

# References

<div id="refs"></div>

\newpage

# Figures {-}

# Appendix {-}

```{r, child = "appendix.rmd"}
```

