---
title: "Results"
author: "Mona Mousavi"
output: html_document
---

```{r}
raw_data <- readRDS("/Users/mmousavi2/Dropbox/ResearchProjects/Cross-Validation-EONR-OFE/Shared/Data/raw_sim_data.rds")
```


```{r}
all_reg_data <-
  raw_data$reg_data[[1]] %>%
  unnest(data) %>%
  data.table() %>%
  .[, .(sim, aunit_id, b0, b1, b2, Nk)]
```


# Whole-field analysis

## Combine the results and calcualte profit deficit


```{r}
results_whole <-
  list.files(
    "/Users/mmousavi2/Dropbox/ResearchProjects/Cross-Validation-EONR-OFE/Shared/Results/WholeField",
    full.names = TRUE
  ) %>%
  purrr::map(readRDS) %>%
  rbindlist() %>%
  all_reg_data[., on = c("aunit_id", "sim")] %>%
  .[, yield_opt := gen_yield_QP(b0, b1, b2, Nk, opt_N)] %>%
  .[, yield_opt_hat := gen_yield_QP(b0, b1, b2, Nk, opt_N_hat)] %>%
  .[, pi_opt := pCorn * yield_opt - pN * opt_N] %>%
  .[, pi_opt_hat := pCorn * yield_opt_hat - pN * opt_N_hat] %>%
  .[, pi_deficit := pi_opt_hat - pi_opt] %>%
  .[order(sim), ]
```

## Summarize the results by sim and method


Find averate RMSE of EONR and $\pi_{deficit}$ and rank methods by sim based on RMSE of EONR.
```{r}
sum_results_whole <-
  results_whole %>%
  .[, N_dif := opt_N_hat - opt_N] %>%
  .[, .(
    rmse_eonr_true = sqrt(mean(N_dif^2)),
    pi_deficit = mean(pi_deficit)
  ), by = .(sim, method)] %>%
  #--- ranking of rmse eonr ---#
  .[order(sim, rmse_eonr_true), ] %>%
  .[, eonr_rank_true := seq(.N), by = sim] %>%
  .[, eonr_selected_true := ifelse(eonr_rank_true == 1, 1, 0)]
```



# Ranking of Candidate ML Models Trained on the entire dataset visualization

```{r}
(
  g_true_rank_rmse_eonr <-
    sum_results_whole[, .(num_selected = sum(eonr_selected_true)), by = method] %>%
    ggplot(.) +
    geom_bar(aes(y = num_selected, x = method), stat = "identity")
)
```

```{r}
deficit <- 
sum_results_whole %>% 
  .[order(sim, pi_deficit), ] %>%
  .[, deficit_rank := seq(.N), by = sim] %>%
  .[, deficit_selected := ifelse(deficit_rank == 5, 1, 0)]

```
# prifit deficit visualization

```{r}
(
  deficit_visualization <-
    deficit[, .(num_selected = sum(deficit_selected)), by = method] %>%
    ggplot(.) +
    geom_bar(aes(y = num_selected, x = method), stat = "identity")
)

```

```{r}
results_dir <- paste0("/Users/mmousavi2/Dropbox/ResearchProjects/Cross-Validation-EONR-OFE/Shared/Results/sim_results_num_repeats_", num_repeats, "_num_folds_", num_folds)
num_repeats=5
num_folds=5

gam_results <-
  list.files(
    results_dir,
    full.names = TRUE
  ) %>%
  .[str_detect(., "gam")] %>%
  purrr::map(readRDS) %>%
  rbindlist(fill = TRUE)

sum_results_gam <-
  gam_results %>%
  #--- average opt_N by fold ---#
  # opt_N_gam is the same for all the observations
  # within a fold
  .[, .(opt_N_gam = mean(opt_N_gam), opt_N = mean(opt_N)), by = .(sim, split_id)] %>%
  .[, opt_N_dif := opt_N - opt_N_gam] %>%
  .[, rmse_local_eonr := sqrt(mean(opt_N_dif^2)), by = sim]

```

# gam and true visualization 

```{r}
(
  gam_true_visualization <- ggplot(sum_results_gam, aes(x= opt_N, y= opt_N_gam))+
  geom_point(colour= I("gray"))+
  geom_abline(slope = 1, intercept = 0) +
  xlim(50 , 300) +
  ylim(50 , 300)
)
```

# Yield based selection

```{r}
# main results
main_results <-
  list.files(
    results_dir,
    full.names = TRUE
  ) %>%
  .[!str_detect(., "train_test|gam")] %>%
  purrr::map(readRDS) %>%
  rbindlist(fill = TRUE)

# main sum results
main_sum_results <-
  main_results %>%
  .[, N_dif := opt_N_hat - opt_N] %>%
  .[, yield_dif := yield_hat - yield] %>%
  .[, .(
    #--- rmse by fold ---#
    rmse_eonr_true = sqrt(mean(N_dif^2)),
    rmse_yield = sqrt(mean(yield_dif^2)),
    #--- average estimated EONR ---#
    opt_N_hat = mean(opt_N_hat)
  ),
  by = .(sim, method, split_id)
  ] %>%
  .[order(sim), ]

# combined results 
combined_results <-
  sum_results_gam[main_sum_results, on = c("sim", "split_id")] %>%
  .[, opt_N_dif_select := opt_N_hat - opt_N_gam] %>%
  .[, .(
    rmse_eonr_gam = sqrt(mean(opt_N_dif_select^2)),
    rmse_yield = mean(rmse_yield)
  ), by = .(sim, method)]

# selection rank
selection_ranks <-
  combined_results %>%
  .[order(sim, rmse_eonr_gam), ] %>%
  #--- within-sim rank based on local EONR prediction ---#
  .[, eonr_rank := seq(.N), by = sim] %>%
  .[, eonr_selected_gam := ifelse(eonr_rank == 1, 1, 0)] %>%
  .[order(sim, rmse_yield), ] %>%
  #--- within-sim rank based on yield prediction ---#
  .[, yield_rank := seq(.N), by = sim] %>%
  .[, yield_selected := ifelse(yield_rank == 1, 1, 0)]
```

# yield based selection visualization

```{r}
(
yield_based_visualization <- selection_ranks[, .(num_selected=sum(yield_selected)), by= method] %>%
  ggplot(.) +
  geom_bar(aes(y=num_selected, x= method), stat = "identity")
)
```

# Local EONR selection visualization

```{r}
(
Local_EONR_based_visualization <- selection_ranks[, .(num_selected=sum(eonr_selected_gam)), by= method] %>%
  ggplot(.) +
  geom_bar(aes(y=num_selected, x= method), stat = "identity")
)
```
# yield-based and Local EONR vs True EONR 

```{r}
library(tidyr)

comp_results_long <- comp_results[[6]][[4]] %>%
  pivot_longer(cols = c(`Local EONR prediction`, `Yield prediction`), names_to = "Prediction", values_to = "Value")
```

```{r}
(
graph <- ggplot(comp_results_long, aes(x = eonr_rank_true, y= Value, fill= Prediction)) +
  geom_bar(stat = "identity", position = "dodge", alpha= 0.5, width = 0.4)+
  labs(x = "eonr_rank_true", y = "Value", fill="5_fold_5_repeats") + 
  scale_fill_manual(values = c("Local EONR prediction" = "blue" , "Yield prediction" = "red")) +
  theme_minimal()
)
```

# The impact of the number of folds and repeats 

```{r}
generate_graph <- function(data, plot_title) {
  comp_results_long <- data %>%
    pivot_longer(cols = c(`Local EONR prediction`, `Yield prediction`), names_to = "Prediction", values_to = "Value")
  
  graph <- ggplot(comp_results_long, aes(x = eonr_rank_true, y = Value, fill = Prediction)) +
    geom_bar(stat = "identity", position = "dodge", alpha = 0.5, width = 0.4) +
    labs(x = "eonr_rank_true", y = "num_selected", fill = plot_title) +
    scale_fill_manual(values = c("Local EONR prediction" = "blue", "Yield prediction" = "red")) +
    theme_minimal() 

  return(graph)
}

library(gridExtra)

# Generate the graphs
graph1 <- generate_graph(comp_results[[6]][[1]], "5_folds_1_repeats")
graph2 <- generate_graph(comp_results[[6]][[2]], "7_folds_1_repeats")
graph3 <- generate_graph(comp_results[[6]][[3]], "10_folds_1_repeats")
graph4 <- generate_graph(comp_results[[6]][[4]], "5_folds_5_repeats")
graph5 <- generate_graph(comp_results[[6]][[5]], "7_folds_5_repeats")
graph6 <- generate_graph(comp_results[[6]][[6]], "10_folds_5_repeats")
graph7 <- generate_graph(comp_results[[6]][[7]], "5_folds_10_repeats")
graph8 <- generate_graph(comp_results[[6]][[8]], "7_folds_10_repeats")
graph9 <- generate_graph(comp_results[[6]][[9]], "10_folds_10_repeats")
```

# Different folds and repeats visualization 

```{r}
# Arrange the plots in a grid
grid.arrange(graph1, graph2, graph3, graph4, graph5, graph6)
grid.arrange(graph7, graph8, graph9)

```





