---
title: Generate simulation data
---

# Preparation

```{r}
# === Packages ===#
library(data.table)
library(tidyverse)
# devtools::install_github("tmieno2/pasim")
library(pasim)
```

## Main simulation data

# Generate simulation data

```{r}
#| eval: false 

set.seed(278543)

sim_data <-
  pasim::gen_fields(
    plot_length = 12, # the length of a plot (in number of cells)
    plot_width = 3, # the width of a plot (in number of cells)
    cell_buffer = 1,
    aunit_length = 2, # the length of an analysis unit (in number of cells)
    aunit_width = 3, # the width of an analysis unit (in number of cells)
    cell = 6, # the length of a cell in meter
    #* how wide the field is
    # field_col = c(36, 72, 144), # the number of cell columns
    field_col = 144, # the number of cell columns
    #* how tall the field is
    field_row = 72 # the number of row columns
  ) %>%
  #--- add trial design layout ---#
  pasim::assign_trial_design(
    design = "Latin Square Fixed 5"
  ) %>%
  #--- generate true field parameters ---#
  mutate(field_pars = list(
    pasim::gen_field_parameters(
      field_sf,
      sp_range = 600,
      gstat_model = "Sph",
      nsim = 500
    )
  )) %>%
  #--- generate trial design ---#
  mutate(trial_design = list(
    pasim::gen_trial_design(field_sf, field_pars, design_name, num_treatments, Nk_minus = 40, Nk_plus = 20)
  )) %>%
  #--- generate regression data ---#
  mutate(reg_data = list(
    pasim::gen_analysis_data(field_pars, field_sf, field_au_sf, trial_design)
  )) %>%
  #--- create the weight matrix if necessary ---#
  mutate(weight_matrix = list(
    pasim::gen_weight_matrix(reg_data, cutoff = 50)
  ))

#* save the data
saveRDS(sim_data, here::here("data/main/raw_sim_data.rds"))
```

## Save simulation data separately

```{r}
sim_data <-
  readRDS(here::here("data/main/raw_sim_data.rds")) %>%
  data.table()
```

Weight matrix for spatial error model:

```{r}
saveRDS(sim_data$weight_matrix[[1]], here::here("data/main/weight_matrix.rds"))
```

Field `sf`:

```{r}
saveRDS(sim_data$field_au_sf[[1]], here::here("data/main/field_au_sf.rds"))
```

Simulation data:

```{r}
reg_data_all <- 
  sim_data$reg_data[[1]] %>%
  .[, file_path := paste0("data/main/individual-fields/sim_data_", sim, ".rds")]  

lapply(
  1:nrow(reg_data_all),
  function(x) {
    saveRDS(
      reg_data_all[x, .(sim, data)],
      here::here(reg_data_all[x, file_path])
    )
  }
)
```

Save file path data:

```{r}
sim_data_file_path <- reg_data_all[, .(sim, file_path)]
saveRDS(sim_data_file_path, here::here("data/main/sim_data_file_path.rds"))
```

Single file contains simulation data for single iteration. This is more memory efficient than loading a single file that contains all the simulation data and filter for a particular simulation in the simulation loop later.

## Quick visualization of the data

```{r}
sim_data$reg_data[[1]]$data[[1]] %>%
  sf::st_as_sf() %>%
  ggplot() +
  geom_sf(aes(fill = Nk_1)) +
  scale_fill_viridis_c()
```

# Data for testing the impact of the spatial correlation of the data

## Objective

The data generated here is used to examine how our selection approach performs if the data has no spatial correlation.

## Generate data

```{r}
#| eval: false
 
set.seed(4503543)

sim_data_no_sp <-
  pasim::gen_fields(
    plot_length = 12, # the length of a plot (in number of cells)
    plot_width = 3, # the width of a plot (in number of cells)
    cell_buffer = 1,
    aunit_length = 2, # the length of an analysis unit (in number of cells)
    aunit_width = 3, # the width of an analysis unit (in number of cells)
    cell = 6, # the length of a cell in meter
    #* how wide the field is
    # field_col = c(36, 72, 144), # the number of cell columns
    field_col = 144, # the number of cell columns
    #* how tall the field is
    field_row = 72 # the number of row columns
  ) %>%
  #--- add trial design layout ---#
  pasim::assign_trial_design(
    design = "Latin Square Fixed 5"
  ) %>%
  #--- generate true field parameters ---#
  mutate(field_pars = list(
    pasim::gen_field_parameters(
      field_sf,
      sp_range = 30,
      gstat_model = "Sph",
      nsim = 500
    )
  )) %>%
  #--- generate trial design ---#
  mutate(trial_design = list(
    pasim::gen_trial_design(field_sf, field_pars, design_name, num_treatments, Nk_minus = 40, Nk_plus = 20)
  )) %>%
  #--- generate regression data ---#
  mutate(reg_data = list(
    pasim::gen_analysis_data(field_pars, field_sf, field_au_sf, trial_design)
  )) %>%
  #--- create the weight matrix if necessary ---#
  mutate(weight_matrix = list(
    pasim::gen_weight_matrix(reg_data, cutoff = 50)
  ))

#* save the data
saveRDS(sim_data_no_sp, here::here("data/no-sp/raw_sim_data.rds"))
```

## Save simulation data separately

```{r}
sim_data_no_sp <-
  readRDS(here::here("data/no-sp/raw_sim_data.rds")) %>%
  data.table()
```

Weight matrix for spatial error model:

```{r}
saveRDS(sim_data_no_sp$weight_matrix[[1]], here::here("data/no-sp/weight_matrix.rds"))
```

Field `sf`:

```{r}
saveRDS(sim_data_no_sp$field_au_sf[[1]], here::here("data/no-sp/field_au_sf.rds"))
```

Simulation data:

```{r}
reg_data_all <- 
  sim_data_no_sp$reg_data[[1]] %>%
  .[, file_path := paste0("data/no-sp/individual-fields/sim_data_no_sp_", sim, "_.rds")]

lapply(
  1:nrow(reg_data_all),
  function(x) {
    saveRDS(
      reg_data_all[x, .(sim, data)],
      here::here(reg_data_all[x, file_path])
    )
  }
)
```

Save file path data:

```{r}
sim_data_file_path <- reg_data_all[, .(sim, file_path)]
saveRDS(sim_data_file_path, here::here("data/no-sp/sim_data_file_path.rds"))
```

Single file contains simulation data for single iteration. This is more memory efficient than loading a single file that contains all the simulation data and filter for a particular simulation in the simulation loop later.

## Quick visualization of the data

```{r}
sim_data_no_sp$reg_data[[1]]$data[[1]] %>%
  sf::st_as_sf() %>%
  ggplot() +
  geom_sf(aes(fill = Nk_1)) +
  scale_fill_viridis_c()
```

As can be seen in the figure, the variable has no spatial correlation.