---
title: "Run Simulations"
---

# Objective 

+ Test if the cross validation method based on local EONR can select the right model (the best in predicting EONR)
  - local EONR (GAM) vs EONR estimates from ML-based methods
+ How do we check whether our method is working or not (comparing with true EONR) 
+ How does the number of folds and repeats affect the usefulness of our cross-validation approach?

# Simulation setup

## Data

```{r}
sim_raw_data_files <- readRDS(here::here("data/main/sim_data_file_path.rds"))

field_au_sf <-
  readRDS(here::here("data/main/field_au_sf.rds")) %>%
  st_as_sf()
```



## Set up simulations (global variables)

```{r}
x_vars <-
  c(
    "b1_1_1", "b1_1_2", "b1_2_1", "b1_2_2",
    "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
    "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2"
  )

pCorn <- 6.25 / 25.4 # $/kg
pN <- 1 / 0.453592 # $/kg
```

# VRA for the whole field by method
```{r, eval = FALSE}
#| eval: false

pbmclapply(
  1:length(sim_raw_data_files),
  #--- loop over fields (sim) ---#
  function(x) {
    print(paste0("Working on ", x, "/", length(sim_raw_data_files)))
    set.seed(835402)
    find_vra_single_whole_field(
      data_file_path = sim_raw_data_files[x],
      x_vars = x_vars,
      models = c("brf", "rf", "lm", "se", "cf"),
      results_path = "results/main/true-best-model"
    )
  },
  mc.cores = min(parallel::detectCores() - 4, 8),
  mc.preschedule = FALSE
)
```

# Run model-selection simulations

```{r}
sim_cases <-
  data.table::CJ(
    num_folds = c(5, 10, 20),
    num_repeats = c(1, 5, 10)
  )

saveRDS(sim_cases, here::here("results/main/sim_cases.rds"))
```

```{r}
#| eval: false

lapply(
  1:nrow(sim_cases),
  \(x) {
    model_selection_sim(
      data_files = sim_raw_data_files,
      field_sf = field_au_sf,
      models = c("lm", "se", "rf", "brf", "cf", "gam"),
      num_repeats = sim_cases[x, num_repeats],
      num_folds = sim_cases[x, num_folds],
      num_cores = min(parallel::detectCores() - 4, 16),
      results_root_dir = "results/main",
      seed = 974345
    )
  }
)
```





