---
title: "Make figures and tables"
date: "2023-02-07"
output: html_document
---

# Main simulation results

```{r}
results_folder <- "results/main"
```

## Load the main results

```{r}
sum_results_whole <-
  readRDS(file.path(results_folder, "sum_results_whole.rds")) %>%
  .[, method := case_when(
    method == "S-learner (SE)" ~ "SE",
    method == "R-learner (CF)" ~ "CF",
    method == "S-learner (BRF)" ~ "BRF",
    method == "S-learner (Linear)" ~ "LM",
    method == "S-learner (RF)" ~ "RF"
  )] %>%
  .[, method := factor(method, levels = c("LM", "SE", "RF", "BRF", "CF"))]

comp_results_main <-
  readRDS(file.path(results_folder, "comp_results.rds")) %>%
  data.table()

sum_results_gam <- readRDS(file.path(results_folder, "sum_results_gam.rds"))
```

## Selection accuracy table

```{r}
accuracy_table <-
  comp_results_main %>%
  .[, .(num_folds, num_repeats, comp_summary)] %>%
  tidyr::unnest() %>%
  data.table() %>%
  # .[eonr_selected_true == 1, ] %>%
  .[, .(
    num_selected_true = sum(eonr_selected_true),
    #--- number of times eonr-based selection correctly chose the best model by model ---#
    num_selected_leonr_correct = sum(eonr_selected_true == 1 & eonr_selected_gam),
    num_selected_leonr = sum(eonr_selected_gam),
    #--- number of times yield-based selection correctly chose the best model by model ---#
    num_selected_yield_correct = sum(eonr_selected_true == 1 & yield_selected),
    num_selected_yield = sum(yield_selected)
  ),
  by = .(method, num_folds, num_repeats)
  ] %>%
  .[, method := case_when(
    method == "S-learner (SE)" ~ "SE",
    method == "R-learner (CF)" ~ "CF",
    method == "S-learner (BRF)" ~ "BRF",
    method == "S-learner (Linear)" ~ "LM",
    method == "S-learner (RF)" ~ "RF"
  )] %>%
  .[, method := factor(method, levels = c("LM", "SE", "RF", "BRF", "CF"))] %>%
  .[order(method), ]

main_accuracy_data <-
  accuracy_table[num_folds == 10 & num_repeats == 5, ] %>%
  .[, leonr_based := paste0(num_selected_leonr_correct, " (", num_selected_leonr, ")")] %>%
  .[, yield_based := paste0(num_selected_yield_correct, " (", num_selected_yield, ")")] %>%
  .[, .(method, num_selected_true, leonr_based, yield_based)]

main_accuracy_table <-
  flextable(main_accuracy_data) %>%
  align(j = 2:4, align = "center") %>%
  set_header_labels(
    values = list(
      method = "Method",
      num_selected_true = "True optimal",
      leonr_based = "LEONR-based selection",
      yield_based = "Yield-based selection"
    )
  ) %>%
  autofit()

saveRDS(main_accuracy_table, here::here("writing/figures-tables/main_selection_accuracy_table.rds"))

saveRDS(accuracy_table, here::here("writing/figures-tables/selection_accuracy_table.rds"))
```

## Performance of candidate models: true, yield-based, EONR-based

```{r}
g_ranking <-
  accuracy_table[num_folds == 10 & num_repeats == 5, ] %>%
  .[, .(method, num_selected_true, num_selected_leonr, num_selected_yield)] %>%
  melt(id.vars = "method") %>%
  .[, select_type := case_when(
    variable == "num_selected_true" ~ "True",
    variable == "num_selected_leonr" ~ "Local EONR",
    variable == "num_selected_yield" ~ "Yield"
  )] %>%
  .[, select_type := factor(select_type, levels = c("True", "Local EONR", "Yield"))] %>%
  ggplot(.) +
  geom_bar(
    aes(y = value, x = method, fill = select_type),
    stat = "identity",
    position = "dodge"
  ) +
  scale_fill_viridis_d() +
  theme_bw() +
  labs(x = "Model", y = "Count", fill = "Selection Type") +
  theme(
    legend.position = "bottom",
    legend.title = element_text(vjust = 0.5)
  )

ggsave(
  "writing/figures-tables/g_ranking.png",
  g_ranking,
  width = 6,
  height = 3.5,
  dpi = 400
)
```

## Profit loss

```{r}
profit_loss_data <-
  comp_results_main[, .(num_folds, num_repeats, loss_data)] %>%
  tidyr::unnest() %>%
  data.table() %>%
  .[, .(sim, num_folds, num_repeats, e_pi_loss, y_pi_loss)] %>%
  melt(id.var = c("sim", "num_folds", "num_repeats")) %>%
  .[, selection := case_when(
    variable == "e_pi_loss" ~ "LEONR-based Selection",
    variable == "y_pi_loss" ~ "Yield-based Selection"
  )]
```

### Main case

```{r}
(
g_pi_loss <-
  ggplot(profit_loss_data[num_folds == 10 & num_repeats == 5, ]) +
  geom_histogram(
    aes(
      x = value,
      y = ifelse(
        after_stat(count) > 0, after_stat(count), NA
      )
    ),
    color = "blue",
    fill = "white"
  ) +
  facet_wrap(selection ~ ., ncol = 1) +
  ylab("Number of iterations") +
  xlab("Profit loss relative to the true best model ($/acre)") +
  theme_bw()
)

ggsave(
  here::here("writing/figures-tables/g_pi_loss.png"),
  g_pi_loss,
  dpi = 300,
  width = 6,
  height = 3.5
)
```

## Correlation Between GAM-Estimated EONR and True EONR

### Main case

```{r}
(
gam_leonr_fit_main <-
  ggplot(sum_results_gam[num_folds == 10 & num_repeats == 5, ]) +
  geom_point(
    aes(x = opt_N, y = opt_N_gam),
    size = 0.5
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    linetype = "dashed",
    color = "red"
  ) +
  xlim(50, 300) +
  ylim(50, 300) +
  ylab("True optimal Local EONR (lb/acre)") +
  xlab("GAM-estimated optimal Local EONR (lb/acre)") +
  theme_bw() +
  theme(
    legend.position = "bottom"
  )
)

ggsave(
  "writing/figures-tables/g_gam_leonr.png",
  gam_leonr_fit_main,
  width = 5,
  height = 3.5,
  dpi = 300
)
```

### All cases

```{r}
(
gam_leonr_fit_all <-
  ggplot(sum_results_gam) +
  geom_point(
    aes(x = opt_N, y = opt_N_gam),
    size = 0.5
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    linetype = "dashed",
    color = "red"
  ) +
  xlim(50, 300) +
  ylim(50, 300) +
  facet_grid(
    rows = vars(`Number of Folds` = num_folds),
    cols = vars(`Number of Repeats` = num_repeats),
    labeller = labeller(
      `Number of Folds` = label_both,
      `Number of Repeats` = label_both
    )
  ) +
  ylab("True optimal Local EONR (lb/acre)") +
  xlab("GAM-estimated optimal Local EONR (lb/acre)") +
  theme_bw() +
  theme(
    legend.position = "bottom"
  )
)
```

## The impact of different fold repeat combination on local EONR selection and yield selection method

```{r}
#--- ranking based on LEONR ---#
perf_ranking_e <-
  comp_results_main[, .(num_folds, num_repeats, selection_perf_rank_LE)] %>%
  tidyr::unnest(selection_perf_rank_LE) %>%
  data.table() %>%
  .[, selection_method := "Based on Local EONR"]

#--- ranking based on Yield ---#
perf_ranking_y <-
  comp_results_main[, .(num_folds, num_repeats, selection_perf_rank_Y)] %>%
  tidyr::unnest(selection_perf_rank_Y) %>%
  data.table() %>%
  .[, selection_method := "Based on Yield"]

# Merge the two data frames into one
perf_ranking_combined <- rbind(perf_ranking_e, perf_ranking_y)

# Plot the combined data using dodge position and refined colors
(
g_sensitivity_fold_repeat <-
  ggplot(perf_ranking_combined) +
  geom_bar(aes(y = N, x = eonr_rank_true, fill = selection_method), stat = "identity", position = "dodge") +
  scale_fill_viridis_d() + # Set colors
  facet_grid(
    rows = vars(`Number of Folds` = num_folds), cols = vars(`Number of Repeats` = num_repeats),
    labeller = labeller(`Number of Folds` = label_both, `Number of Repeats` = label_both)
  ) +
  labs(
    x = "True ranking of the selected model",
    y = "Number of iterations",
    fill = "Model Selection Approach"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") + # Move the legend to the bottom
  theme(strip.text = element_text(size = 9)) +
  theme(
    legend.position = "bottom",
    # plot.title = element_text(size = 10, face = "bold"),  # Title appearance
    # plot.subtitle = element_text(size = 12),
    axis.title.x = element_text(size = 12), # X-axis label appearance
    axis.title.y = element_text(size = 12), # Y-axis label appearance
    legend.title = element_text(size = 12), # Legend title appearance
    legend.text = element_text(size = 9) # Legend text appearance
  ) +
  theme(axis.title = element_text(size = 12))
)


ggsave(
  here::here("writing/figures-tables/g_sensitivity_fold_repeat.png"),
  g_sensitivity_fold_repeat,
  width = 6,
  height = 6,
  dpi = 300
)
```

# Simulation results with data with no spatial correlation

## Load the main results

```{r}
sum_results_whole <-
  readRDS(here::here("results/no-sp/sum_results_whole.rds")) %>%
  .[, method := case_when(
    method == "S-learner (SE)" ~ "SE",
    method == "R-learner (CF)" ~ "CF",
    method == "S-learner (BRF)" ~ "BRF",
    method == "S-learner (Linear)" ~ "LM",
    method == "S-learner (RF)" ~ "RF"
  )] %>%
  .[, method := factor(method, levels = c("LM", "SE", "RF", "BRF", "CF"))]

comp_results_nosp <-
  readRDS(here::here("results/no-sp/comp_results.rds")) %>%
  data.table()
```

## Selection accuracy table 

```{r}
accuracy_table_nosp <-
  comp_results_nosp %>%
  .[, .(num_folds, num_repeats, comp_summary)] %>%
  tidyr::unnest() %>%
  data.table() %>%
  # .[eonr_selected_true == 1, ] %>%
  .[, .(
    num_selected_true = sum(eonr_selected_true),
    #--- number of times eonr-based selection correctly chose the best model by model ---#
    num_selected_leonr_correct = sum(eonr_selected_true == 1 & eonr_selected_gam),
    num_selected_leonr = sum(eonr_selected_gam),
    #--- number of times yield-based selection correctly chose the best model by model ---#
    num_selected_yield_correct = sum(eonr_selected_true == 1 & yield_selected),
    num_selected_yield = sum(yield_selected)
  ),
  by = .(method, num_folds, num_repeats)
  ] %>%
  .[, method := case_when(
    method == "S-learner (SE)" ~ "SE",
    method == "R-learner (CF)" ~ "CF",
    method == "S-learner (BRF)" ~ "BRF",
    method == "S-learner (Linear)" ~ "LM",
    method == "S-learner (RF)" ~ "RF"
  )] %>%
  .[, method := factor(method, levels = c("LM", "SE", "RF", "BRF", "CF"))] %>%
  .[order(method), ]

main_accuracy_data <-
  accuracy_table_nosp[num_folds == 10 & num_repeats == 5, ] %>%
  .[, leonr_based := paste0(num_selected_leonr_correct, " (", num_selected_leonr, ")")] %>%
  .[, yield_based := paste0(num_selected_yield_correct, " (", num_selected_yield, ")")] %>%
  .[, .(method, num_selected_true, leonr_based, yield_based)]

(
main_accuracy_table_nosp <-
  flextable(main_accuracy_data) %>%
  align(j = 2:4, align = "center") %>%
  set_header_labels(
    values = list(
      method = "Method",
      num_selected_true = "True optimal",
      leonr_based = "LEONR-based selection",
      yield_based = "Yield-based selection"
    )
  ) %>%
  autofit()
)

saveRDS(main_accuracy_table_nosp, here::here("writing/figures-tables/selection_accuracy_table_no_sp_ft.rds"))

saveRDS(accuracy_table_nosp, here::here("writing/figures-tables/selection_accuracy_table_no_sp.rds"))
```

## Profit loss

```{r}
profit_loss_data_nosp <-
  comp_results_nosp[, .(num_folds, num_repeats, loss_data)] %>%
  tidyr::unnest() %>%
  data.table() %>%
  .[, .(sim, num_folds, num_repeats, e_pi_loss, y_pi_loss)] %>%
  melt(id.var = c("sim", "num_folds", "num_repeats")) %>%
  .[, selection := case_when(
    variable == "e_pi_loss" ~ "LEONR-based Selection",
    variable == "y_pi_loss" ~ "Yield-based Selection"
  )]
```

### Main case

```{r}
(
 g_pi_loss_nosp <-
  ggplot(profit_loss_data_nosp) +
  geom_histogram(
    aes(
      x = value,
      y = ifelse(
        after_stat(count) > 0, after_stat(count), NA
      )
    ),
    color = "blue",
    fill = "white"
  ) +
  facet_wrap(selection ~ ., ncol = 1) +
  ylab("Number of iterations") +
  xlab("Profit loss relative to the true best model ($/acre)") +
  theme_bw() 
)


ggsave(
  here::here("writing/figures-tables/g_pi_loss_nosp.png"),
  g_pi_loss_nosp,
  dpi = 300,
  width = 6,
  height = 3.5
)
```


# Misc

## Spatial cross validation (example of a fold with train and test data)

```{r}
#--- first simulation ---#
whole_data <-
  readRDS(here::here("Shared/Data/SimData/sim_data_1.rds"))$data[[1]] %>%
  data.table()

#--- train or test ---#
train_test_split_q <-
  readRDS(file.path(results_folder, "sim_results_num_repeats_1_num_folds_5/train_test_split.rds"))

spatial_folds_q <-
  train_test_split_q %>%
  rowwise() %>%
  mutate(training_data = list(
    whole_data[aunit_id %in% training_ids, .(aunit_id, geometry)] %>%
      .[, type := "Training"]
  )) %>%
  mutate(test_data = list(
    whole_data[aunit_id %in% test_ids, .(aunit_id, geometry)] %>%
      .[, type := "Test"]
  )) %>%
  dplyr::mutate(combined_data = list(
    rbind(training_data, test_data)
  )) %>%
  dplyr::select(split_id, combined_data) %>%
  tidyr::unnest(cols = combined_data) %>%
  sf::st_as_sf() %>%
  dplyr::mutate(split_txt := paste0("Fold ", split_id))

(
g_split_example <-
  ggplot(spatial_folds_q) +
  geom_sf(aes(fill = type), color = NA) +
  facet_wrap(split_txt ~ ., ncol = 2) +
  scale_fill_discrete(
    name = "Role of the data",
    guide = guide_legend(title.position = "top", nrow = 1)
  ) +
  theme_void() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.75, 0.2),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12)
  )
)

ggplot2::ggsave(
  here::here("writing/figures-tables/g_split_example.png"),
  g_split_example,
  dpi = 300,
  height = 6,
  width = 6
)
```

# Spatial cross validation (example: 10 fold) 

```{r}
#--- first simulation ---#
whole_data <-
  readRDS(here::here("data/main/sim_data_1.rds"))$data[[1]] %>%
  data.table()

#--- train or test ---#
train_test_split_q <-
  readRDS(file.path(results_folder, "sim_results_num_repeats_1_num_folds_10/train_test_split.rds"))

spatial_folds_q <-
  train_test_split_q %>%
  rowwise() %>%
  mutate(training_data = list(
    whole_data[aunit_id %in% training_ids, .(aunit_id, geometry)] %>%
      .[, type := "Training"]
  )) %>%
  mutate(test_data = list(
    whole_data[aunit_id %in% test_ids, .(aunit_id, geometry)] %>%
      .[, type := "Test"]
  )) %>%
  dplyr::mutate(combined_data = list(
    rbind(training_data, test_data)
  )) %>%
  dplyr::select(split_id, combined_data) %>%
  tidyr::unnest(cols = combined_data) %>%
  sf::st_as_sf() %>%
  dplyr::mutate(split_txt := paste0("Fold ", split_id))

spatial_folds_q <- spatial_folds_q %>%
  arrange(split_id) %>%  #  correct order in dataset
  mutate(split_txt = factor(split_txt, levels = unique(split_txt)))  # convert to ordered factor

(
g_split_example_10_folds <-
  ggplot(spatial_folds_q) +
  geom_sf(aes(fill = type), color = NA) +
  facet_wrap(~split_txt, ncol = 3)  +
  scale_fill_discrete(
    name = "Role of the data",
    guide = guide_legend(title.position = "top", nrow = 1)
  ) +
  theme_void() +
  theme(
    legend.position = "bottom",  
    legend.justification = c(0, 0),  # Aligns it to the left
    legend.box = "horizontal", 
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12)
  )
)

ggplot2::ggsave(
  here::here("GitControlled/Writing/figures-tables/g_split_example_10_folds.png"),
  g_split_example_10_folds,
  dpi = 300,
  height = 6,
  width = 6
)
```
