---
title: "Run Simulations"
author: "Mona Mousavi"
date: "2023-02-07"
output: html_document
---

# Objective 

+ To see if the cross validation method based on local EONR can select the right model (the best in predicting EONR)
  - local EONR (GAM) vs EONR estaimtes from ML-based methods
+ How do we check whether our method is working or not (comparing with true EONR) 
+ How does the number of folds and repetas affect the usefulness of our cross-validation approach?

# Preparation

```{r}
library(tidyverse)
list.files(here::here("GitControlled/Codes/functions/"), full.names = TRUE) %>%
  lapply(., source)
```

# Simulation setup

## Data

```{r}
all_data_files <- list.files(here::here("Shared/Data/SimData"), full.names = TRUE)
```

## Set up simulations (global variables)

```{r}
x_vars <-
  c(
    "theta_b2_2", "theta_b1_2",
    "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
    "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2"
  )

pCorn <- 6.25 / 25.4 # $/kg
pN <- 1 / 0.453592 # $/kg
```

# VRA for the whole field by method
```{r}
models <- c("brf", "rf", "lm", "se", "cf")

pbmclapply(
  1:length(all_data_files),
  #--- loop over fields (sim) ---#
  function(x) {
    find_vra_single_whole_field(
      file_path = all_data_files[x],
      x_vars = x_vars,
      models = models
    )
  },
  mc.cores = 10
)
```

# Run model-selection simulations

```{r}
num_repeats <- 5
num_folds <- 5

#--- create a directory to store the results ---#
results_dir <- paste0("Shared/Results/sim_results_num_repeats_", num_repeats, "_num_folds_", num_folds)
dir.create(results_dir)

#--- create seed for spatial cross-validation ---#
data_seed <-
  data.table(
    file = all_data_files
  ) %>%
  .[, resampling_seed := rnorm(1), by = file]

saveRDS(data_seed, here::here(results_dir, "data_seed.rds"))

data_seed <- readRDS(here::here(results_dir, "data_seed.rds"))

  pbmclapply(
    1:length(all_data_files),
    function(x) {
      model_selection_sim_single_field(
        file_path = data_seed[x, file],
        models = c("lm", "se"),
        results_dir = results_dir,
        resampling_seed = data_seed[x, resampling_seed],
        num_repeats,
        num_folds
      )
    },
    mc.cores = 10
```



