---
title: "Run Simulations"
author: "Mona Mousavi"
date: "2023-02-07"
output: html_document
---

# Objective 

+ To see if the cross validation method based on local EONR can select the right model (the best in predicting EONR)
  - local EONR (GAM) vs EONR estaimtes from ML-based methods
+ How do we check whether our method is working or not (comparing with true EONR) 
+ How does the number of folds and repetas affect the usefulness of our cross-validation approach?

# Preparation

```{r}
library(tidyverse)
list.files(here::here("GitControlled/Codes/functions/"), full.names = TRUE) %>%
  lapply(., source)
```

# Simulation setup

## Data

```{r}
data_files <- list.files(here::here("Shared/Data/SimData"), full.names = TRUE)

field_au_sf <-
  readRDS(here::here("Shared/Data/field_au_sf.rds")) %>%
  st_as_sf()
```

## Set up simulations (global variables)

```{r}
x_vars <-
  c(
    "theta_b2_2", "theta_b1_2",
    "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
    "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2"
  )

pCorn <- 6.25 / 25.4 # $/kg
pN <- 1 / 0.453592 # $/kg
```

# VRA for the whole field by method
```{r, eval = FALSE}
models <- c("brf", "rf", "lm", "se", "cf")

pbmclapply(
  1:length(data_files),
  #--- loop over fields (sim) ---#
  function(x) {
    find_vra_single_whole_field(
      file_path = data_files[x],
      x_vars = x_vars,
      models = models
    )
  },
  mc.cores = 10
)
```

# Run model-selection simulations

## 7 folds, 10 repetas

```{r}
model_selection_sim(
  data_files = data_files,
  field_sf = field_au_sf,
  # models = c("lm", "se", "rf", "brf", "cf", "gam"),
  models = "gam",
  num_repeats = 10,
  num_folds = 7,
  num_cores = 5
)

model_selection_sim(
  data_files = data_files,
  field_sf = field_au_sf,
  models = c("lm", "se"),
  # models = c("lm", "se", "rf", "brf", "cf"),
  num_repeats = 10,
  num_folds = 7,
  num_cores = 10
)

model_selection_sim(
  data_files = data_files,
  field_sf = field_au_sf,
  models = c("rf", "brf", "cf"),
  num_repeats = 10,
  num_folds = 7,
  num_cores = 10
)
```

## 5 folds, 1 repetas

```{r}
set.seed(974345)

model_selection_sim(
  data_files = data_files,
  field_sf = field_au_sf,
  models = c("lm", "se", "rf", "brf", "cf", "gam"),
  num_repeats = 1,
  num_folds = 5,
  num_cores = 10
)
```

## 7 folds, 1 repetas

```{r}
set.seed(974345)

model_selection_sim(
  data_files = data_files,
  field_sf = field_au_sf,
  models = c("lm", "se", "rf", "brf", "cf", "gam"),
  num_repeats = 5,
  num_folds = 7,
  num_cores = 10
)
```



