
---
title: "Make figures and tables"
date: "2023-02-07"
output: html_document
---

# Preparation

## Packages and functions 
```{r}
library(tidyverse)
library(pasim)
list.files(here::here("GitControlled/Codes/functions/"), full.names = TRUE) %>%
  lapply(., source)
```
```{r}
comp_results <-
  readRDS(here::here("Shared/Results/comp_results.rds")) %>%
  data.table()
```

# The actual performance ranking of the model selected by our LEONR-based approach

```{r}
perf_ranking_e <-
  comp_results[, .(num_folds, num_repeats, selection_perf_rank_LE)] %>%
  unnest(selection_perf_rank_LE) %>%
  data.table()

ggplot(perf_ranking_e) +
  geom_bar(aes(y = N, x = eonr_rank_true), stat = "identity") +
  facet_grid(num_folds ~ num_repeats)
```

# The actual performance ranking of the model selected by yield-based selection approach 

```{r}
perf_ranking_y <-
  comp_results[, .(num_folds, num_repeats, selection_perf_rank_Y)] %>%
  unnest(selection_perf_rank_Y) %>%
  data.table()

ggplot(perf_ranking_y) +
  geom_bar(aes(y = N, x = eonr_rank_true), stat = "identity") +
  facet_grid(num_folds ~ num_repeats)
```

# Performance loss  

```{r}
perf_loss_data <-
  comp_results[, .(num_folds, num_repeats, loss_data)] %>%
  unnest(loss_data) %>%
  data.table()
```

## RMSE of EONR (selected versus true best) 

How much difference in rmse of site-speicific EONR prediction between the model selected based on LEONR or Yield and the model that is truly the best in predicting site-speicific EONR.

```{r}
perf_loss_data_eonr <-
  perf_loss_data[, .(sim, num_folds, num_repeats, e_rmse_eonr_loss, y_rmse_eonr_loss)] %>%
  melt(id.var = c("sim", "num_folds", "num_repeats")) %>%
  .[, selection := case_when(
    variable == "e_rmse_eonr_loss" ~ "LEONR-based Selection",
    variable == "y_rmse_eonr_loss" ~ "Yield-based Selection"
  )]

(
  ggplot(perf_loss_data_eonr[num_folds == 7 & num_repeats == 10, ]) +
    geom_histogram(aes(x = value)) +
    facet_grid(selection ~ .) +
    theme_bw()
)
```

##

```{r}
perf_loss_data_pi <-
  perf_loss_data[, .(sim, num_folds, num_repeats, e_pi_loss, y_pi_loss)] %>%
  melt(id.var = c("sim", "num_folds", "num_repeats")) %>%
  .[, selection := case_when(
    variable == "e_pi_loss" ~ "LEONR-based Selection",
    variable == "y_pi_loss" ~ "Yield-based Selection"
  )]

(
  ggplot(perf_loss_data_pi[num_folds == 7 & num_repeats == 10, ]) +
    geom_histogram(aes(x = value)) +
    facet_grid(selection ~ .) +
    theme_bw()
)
```

